---
title: "Covid91 vaccine study Final2024"
author: "Milton Rodas"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "11/26/24" 
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(forcats)
#recode to remove the annoying "X" from the dataframe
FinalData <- FinalDat  %>% select(-one_of("X"))
FinalData <- FinalData %>%
mutate(across(where(is.character), as.factor))
FinalData$treatment <- relevel(FinalData$treatment,ref="placebo")
#FinalData$infected <- relevel(FinalData$infected,ref="OK")
males = filter(FinalData, sex =="M")
```


# Introduction

A new  preventative vaccine (covid921) is under test in clinical trials. Given the nature of this vaccine it is suspected that the drug may exhibit different effectiveness across the variety of subpopulations tracked. Consider population subgroups by gender( guys and gals), drug use, and sexual orientation. Write a complete report that separately considers this drug for each subgroup and your recommendations as to whether people in the subgroup should take the vaccine. Structure your report in four sections each devoted to one of the four subgroups, use null and alternative hypothesis statements and correct statistical verbage when referencing p-values in conclusions.

## Males
###Barplot

```{r}
dd2 <- males %>% group_by(infected,treatment) %>% summarize(count=n()) %>% mutate(prcnt=count/sum(count))


basicC <- ggplot(dd2,aes(x=infected,y=count,fill=treatment))
basicC + geom_bar(stat="identity",position="dodge")

#Now for percentage plot

basicCC <- ggplot(dd2,aes(x=infected,y=prcnt*100,fill=treatment)) 
basicCC + geom_bar(stat="identity", position = "dodge")
```


   This plot represents the population of males and their relationship to getting covid-19 by taking either the vaccine or the placebo. The plot shows that around 68% of males who got covid took the placebo. Whereas about 32% of males who got covid took the vaccine. Therefore, more males who got covid took the placebo, whereas the males who got covid from taking the vaccine were not as likely to contract covid as much. This means that the vaccine seems to be effective for the males in this dataset. 
  There were two plots that came out. The first plot shows two bars for the treatment, either the placebo or the vaccine. Along the x-axis was the amount of people there was, and along the y-axis shows the infected from covid, either placebo or vaccine. It shows the number of people infected from covid or from the placebo. 
  

## Females


## LGBTQ



## Druggies


# Overall Results and Conclusions